\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
reviewing correcting and uploading

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
\medskip
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system. The flow of a fluid over or next to another heavier fluid, can produce flow instabilities. Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.

Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
T is the surface tension and U is a velocity characteristic of the moving interface.

@@

\medskip
In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ... SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN? ... TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}. More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}

\medskip
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system. The flow of a fluid over or next to another heavier fluid, can produce flow instabilities. Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.

\medskip
Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
T is the surface tension and U is a velocity characteristic of the moving interface.

@@

\medskip
In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% keep drafting it %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\red{(THIS SENTENCE IS A BIT CONFUSING ... SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN? ... TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}. More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
